---
title: "Content Based Recommendation System"
author: "Mritunjay And Sunil"
date: "13/10/2019"
output: html_document
---

# Recommended System Techniques on Airbnb (Amsterdam Hotel Recommendation)
# 1. Content Based Recommendation System

### Load all the relevant libraries and Get the working directory and Load the Amsterdam Hotel Airbn data set
```{r}
pacman::p_load(tidyverse, purrr, stringr, data.table, modelr, readxl,caret, corrplot, broom, ggpubr, tm, proxy, MASS,relaimpo, car,interplot, caTools, mice, gbm, reshape2, compiler, recommenderlab, Matrix, knitr,tidyr, dplyr, animation, wordnet, RColorBrewer, wordcloud, SnowballC, topicmodels, ggplot2, cluster, fpc)
getwd()
airbnb = read.csv("airbnb.csv", header=TRUE, sep=",") # transaction format!
names(airbnb) = c(colnames(airbnb))
head(airbnb,1)
```

### Structure of Datasets
```{r}
str(airbnb)
```

### Create a dataset for CF from main airbnb dataset (User_ID, Hotel_ID, Ratings)
```{r}
colnames(airbnb)
```

### Create airbnb_hotels dataframe with features columns to create corpus for text mining along with Hotel ID
```{r}
airbnb_Hotels <- airbnb[, c('Hotel_Id', 'summary', 'space', 'description', 'property_type', 'room_type', 'accommodates', 'bathrooms', 'bedrooms', 'beds', 'bed_type', 'amenities')]
airbnb_Hotels_Unique = airbnb_Hotels[!duplicated(airbnb_Hotels$Hotel_Id), ]
head(airbnb_Hotels_Unique,4)
```

### Now Combined all the features columns for mining
```{r}
airbnb_Hotels_Unique$features_text = paste(airbnb_Hotels_Unique$summary, airbnb_Hotels_Unique$space, airbnb_Hotels_Unique$description, airbnb_Hotels_Unique$property_type, airbnb_Hotels_Unique$room_type, airbnb_Hotels_Unique$accommodates, airbnb_Hotels_Unique$bathrooms, airbnb_Hotels_Unique$bedrooms, airbnb_Hotels_Unique$beds, airbnb_Hotels_Unique$bed_type, airbnb_Hotels_Unique$amenities)
airbnb_Hotels_mining = airbnb_Hotels_Unique[,c("Hotel_Id","features_text")]
write.csv(airbnb_Hotels_mining,"airbnb_Hotels_mining.csv")
head(airbnb_Hotels_mining,2)
```

### Now Create Corpus on features_text
```{r}
HotelStopWord = c(stopwords('english'), "also", "hous", "includ", "well", "around", "fuli", "great", "lot", "apart", "famous", "minut", "amsterdam", "love", "within", "space", "away", "nice", "friend", "need", "best", "use", "find", "miss", "public", "close", "open", "locat", "can", "will", "just", "like")
corpus <- VCorpus(VectorSource(airbnb_Hotels_mining$features_text))

corpusNormalization <- function(corpus) {
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, removeWords, HotelStopWord)
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, stemDocument)
  corpus <- tm_map(corpus, removeWords, HotelStopWord)
  corpus <- tm_map(corpus, stripWhitespace)
 
  return(corpus)
}

corpusNorms = corpusNormalization(corpus)

dtm <- DocumentTermMatrix(corpusNorms)
dtm_ti <- weightTfIdf(dtm)
dtm_ti

mat_ti <- as.matrix(dtm_ti)

### Count the frequency of each concept
CorpusFreq <- colSums(as.matrix(dtm)) #Sum each column
head(CorpusFreq)
```


### Histograms for most occured words
```{r}
wf <- data.frame(term = names(CorpusFreq), occurrences = CorpusFreq)

ggplot(subset(wf, CorpusFreq > 250), aes(term, occurrences, color = term)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Add color on wordcloud for Accident Type Column
```{r}
dark2 <- brewer.pal(6, "Dark2")
wordcloud(names(CorpusFreq), CorpusFreq, max.words=100, rot.per=0.6, colors=dark2)
```

### Find the Frequency of ReportTypeCorpusFreq
```{r}
length(CorpusFreq)   ### [1] 2725

CorpusOrderFreq <- order(CorpusFreq, decreasing = TRUE)

CorpusFreq[head(CorpusOrderFreq,10)]
# kill   fall  injur struck    die   burn 
# 2139   2114   1724   1151   1093    982 

CorpusFreq[tail(CorpusOrderFreq)]
```

```{r}
rownames(airbnb_Hotels_mining) <- 1:nrow(airbnb_Hotels_mining)
dist_mat_cos <- as.matrix(dist(mat_ti, method = "cosine"))
dist_mat_cos_df = data.frame(sort(dist_mat_cos[, 1], decreasing = T)[1:5])
c = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1] 
dist_mat_cos_df


Top1_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top2_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top3_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top4_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top5_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))

for (i in 1:nrow(airbnb_Hotels_mining)) {
  target = airbnb_Hotels_mining[rownames(airbnb_Hotels_mining)[i],1]
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[1])
  Top1_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[2])
  Top2_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[3])
  Top3_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[4])
  Top4_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[5])
  Top5_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
}

df_cb <- data.frame(Top1_Similar_Hotel, 
                    Top2_Similar_Hotel, 
                    Top3_Similar_Hotel, 
                    Top4_Similar_Hotel, 
                    Top5_Similar_Hotel, stringsAsFactors = TRUE)
rownames(df_cb) = airbnb_Hotels_mining[,1]
write.csv(df_cb, file = "Content Based Recommended Hotel For each Hotel using cosine.csv")



dist_mat_cos <- as.matrix(dist(mat_ti, method = "euclidean"))
dist_mat_cos_df = data.frame(sort(dist_mat_cos[, 1], decreasing = T)[1:10])
e = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1] 
dist_mat_cos_df

Top1_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top2_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top3_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top4_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top5_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))

for (i in 1:nrow(airbnb_Hotels_mining)) {
  target = airbnb_Hotels_mining[rownames(airbnb_Hotels_mining)[i],1]
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[1])
  Top1_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[2])
  Top2_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[3])
  Top3_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[4])
  Top4_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[5])
  Top5_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
}

df_cb <- data.frame(Top1_Similar_Hotel, 
                    Top2_Similar_Hotel, 
                    Top3_Similar_Hotel, 
                    Top4_Similar_Hotel, 
                    Top5_Similar_Hotel, stringsAsFactors = TRUE)
rownames(df_cb) = airbnb_Hotels_mining[,1]
write.csv(df_cb, file = "Content Based Recommended Hotel For each Hotel using euclidean.csv")

### correlation is nothing but pearson's correlation
dist_mat_cos <- as.matrix(dist(mat_ti, method = "correlation"))
dist_mat_cos_df = data.frame(sort(dist_mat_cos[, 1], decreasing = T)[1:10])
p = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1] 
dist_mat_cos_df

Top1_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top2_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top3_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top4_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top5_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))

for (i in 1:nrow(airbnb_Hotels_mining)) {
  target = airbnb_Hotels_mining[rownames(airbnb_Hotels_mining)[i],1]
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[1])
  Top1_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[2])
  Top2_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[3])
  Top3_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[4])
  Top4_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[5])
  Top5_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
}

df_cb <- data.frame(Top1_Similar_Hotel, 
                    Top2_Similar_Hotel, 
                    Top3_Similar_Hotel, 
                    Top4_Similar_Hotel, 
                    Top5_Similar_Hotel, stringsAsFactors = TRUE)
rownames(df_cb) = airbnb_Hotels_mining[,1]
write.csv(df_cb, file = "Content Based Recommended Hotel For each Hotel using correlation.csv")

dist_mat_cos <- as.matrix(dist(mat_ti, method = "jaccard"))
dist_mat_cos_df = data.frame(sort(dist_mat_cos[, 1], decreasing = T)[1:10])
j = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1] 
dist_mat_cos_df

Top1_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top2_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top3_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top4_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))
Top5_Similar_Hotel = integer(nrow(airbnb_Hotels_mining))

for (i in 1:nrow(airbnb_Hotels_mining)) {
  target = airbnb_Hotels_mining[rownames(airbnb_Hotels_mining)[i],1]
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[1])
  Top1_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[2])
  Top2_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[3])
  Top3_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[4])
  Top4_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
  
  dist_mat_cos_df = data.frame(sort(dist_mat_cos[, i], decreasing = T)[5])
  Top5_Similar_Hotel[i] = airbnb_Hotels_mining[rownames(dist_mat_cos_df),1]
}

df_cb <- data.frame(Top1_Similar_Hotel, 
                    Top2_Similar_Hotel, 
                    Top3_Similar_Hotel, 
                    Top4_Similar_Hotel, 
                    Top5_Similar_Hotel, stringsAsFactors = TRUE)
rownames(df_cb) = airbnb_Hotels_mining[,1]
write.csv(df_cb, file = "Content Based Recommended Hotel For each Hotel using jaccard.csv")

union(union(union(c,e),p),j)
i1 = intersect(c,e)
i2 = intersect(c,p)
i3 = intersect(c,j)
i4 = intersect(e,p)
i5 = intersect(e,j)
i6 = intersect(p,j)
union(union(union(union(union(i1,i2),i3),i4),i5),i6)
```

### 

View


